---
title: ASML Stock Movement During SPIE Conference
author: Richard Yang
date: '2017-02-26'
categories:
  - R
  - nanomanufacturing
  - conference
tags:
  - R
  - SPIE
---
```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE)
library(Quandl)
library(dygraphs)

```


## Semiconductor Capital Equipment Spending

## SPIE Advanced Lithography Conference

## ASML

### ASML public stock

Pull two year data from Google finacial source. Online website only allow last 9 months for daily data. The Quandl package is able to pull specified data with ticker "NASDAQ_ASML" from 01/01/2015.

```{r data}
ASML <-Quandl("GOOG/NASDAQ_ASML",start_date="2015-01-01",type="ts")

str(ASML)

```

The data can be made interactive with dygraph package. It allow zoom into specific peroid and find stock price of particlar date.
```{r close price}
dygraph(ASML$Close) %>% dyRangeSelector()

```

Last two SPIE conference date:

- 21-25 February 2016
- 22-26 February 2015

Include one weeks prior and post the conference. In both peroid, ASML stock jumpped 
```{r compare}
SPIE.2017 <-Quandl("GOOG/NASDAQ_ASML",start_date="2017-02-20",end_date="2017-03-04", type="ts")

SPIE.2016 <-Quandl("GOOG/NASDAQ_ASML",start_date="2016-02-15",end_date="2016-03-04", type="ts")

SPIE.2015 <-Quandl("GOOG/NASDAQ_ASML",start_date="2015-02-16",end_date="2015-03-05", type="ts")

ASML.SPIE <- cbind(SPIE.2017$Close, SPIE.2016$Close, SPIE.2015$Close)
colnames(ASML.SPIE) <- c("SPIE.2017", "SPIE.2016", "SPIE.2015")

dygraph(ASML.SPIE,ylab="Close", 
        main="ASML Stock movement during SPIE conferences") %>%
   dySeries("SPIE.2017",label="SPIE.2017") %>%
  dySeries("SPIE.2016",label="SPIE.2016") %>%
  dySeries("SPIE.2015",label="SPIE.2015") %>%
  dyOptions(colors = c("blue","brown","green")) %>%
  dyRangeSelector()

```


## Round up

ASML stock motion data has been pulled and compared. It is yet to see how would its stock move duing the coming conference. It would next be interesting to mining what topics has been discussed during the conference and correlation with ASML stock movement.
