---
title: "Moore's Law in Motion"
author: "Richard Yang"
date: '2017-02-19'
categories:
- motion chart
- Moore's law
---
```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.path='fig/',
                      echo=FALSE, warning=FALSE, message=FALSE)
library(readr)
library(readxl)
library(googleVis)
library(ezknitr)

op <- options(gvis.plot.tag='chart')

```

## Objectives
Moore's law has been the golden law to predict the semiconductor device size and guide the long-term planning of semiconductor industry in the last 3 decades. It has been accurately describing a driving force behind technological and economical growth.

This post is to visualize Moore's law in semiconductor manufacturing. 

## Work flow

Main work flow to construct motion chart of Moore's law require following steps:

1. Scape data from credible sources
2. Format data for motion chart
3. Generate motion chart with GoogleVis package
4. Deploy to website with blogdown

## Solution

### Review of Prior Art
Moore's law predicted that chip performance would double every 18 months, a driving force to shrink the device constantly over the time.

The data source of this report would be parsed from Wiki pages, which are reliable and consistent with other published results: [Moore's Law ](https://en.wikipedia.org/wiki/Moore%27s_law), [device dimension](https://en.wikipedia.org/wiki/Semiconductor_device_fabrication) and [transistor counts](https://en.wikipedia.org/wiki/Transistor_count).

The data can be scrapped from html tables directly from R packages. This report start with manual construction of data table from above source.

Motion chart was first demonstrated by Hans Rosling. The chart is made possible by [googleVis package](https://cran.r-project.org/web/packages/googleVis/vignettes/googleVis_examples.html).

### Prepare data 

The data has been manually constructed in as a csv file. A minor issue with testing the notebook chuck and have to manually set the working directory

```{r data}
setwd("D:/Data-Yang/Blog/semiexpert")
node <- read_excel("data/Moore_law.xlsx",sheet="node")
head(node)

```

Basic motion chart can be constructed by passing the time and id variables. To visualize the shrinking of device nodes and increasing transistor counts, it is better to visualize different vendor's technology, such as Intel, TI, IBM and AMD.

### Clean up data:

1. Import html data table from wiki page
2. Remove notes to the year and nodes
3. Format year and process.node to be numeric

### Motion Chart 

This is to illustrate the shrink of device node over time and increasing transistor count. idvar has been set to Designer to illustrate various player over the time. One unique performer is Intel could been seen growth over time.


```{r motion chart, results='asis', tidy=FALSE, echo=TRUE}
M <- gvisMotionChart(node, 
                       idvar="Designer", 
                       timevar="year",
                       xvar="node.nm",
                       yvar="Count")
print(M)

```

Issues found and resolved:

- Display googleVis chart locally: resolved with security setting of [macromedia](http://www.macromedia.com/support/documentation/en/flashplayer/help/settings_manager04.html)
- Settings for rmarkdown "op <- options(gvis.plot.tag='chart')" and place "results='asis'" in the chuck option

## Round up

Moore's law recreated with motion chart and illustrated new players for the industry and their evolution.